\documentclass[12pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage[utf8x]{inputenc}

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
% \usepackage{hyperref}

\usepackage[scale=0.75]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3cm} % Un-comment to change the width of the dates column
% \setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, un-comment to adjust the width of the space allocated to your name

\firstname{Kemal} % Your first name
\familyname{Akkoyun} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Reasoned Software Engineer}
\email{kakkoyun@gmail.com - +49 (173) 238 85 13}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Prinst the CV title

\url{linkedin.com/in/kemalakkoyun} \\
\url{github.com/kakkoyun} \\
\url{stackoverflow.com/story/kakkoyun} \\
\url{kakkoyun.github.io} \\

\vspace{1cm}

\cvitem{}{\textit{Reasoned Software Engineer who has a growth mindset, DevOps Enthusiast who has the necessary skills and mindset, Full-Cycle Engineer and Full-Stack Developer (yes, the "frontend” is not strong with this one). First principle thinker who still believes agile! }}
\cvitem{}{\textit{I build distributed, real-time and message passing based systems at scale. Nowadays, I play with Kubernetes and tools around it and working on advancing my network knowledge and skills. }}
\cvitem{}{\textit{I love learning new programming languages, functional programming, diving deep into runtime systems, infrastructure as code and I've a special interest in automated testing. }}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%  SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills, Merits and Faculties}

\cvitem{\textbf{Soft Skills}}{ Open mindedness. Problem solving. Creativity. Leadership. Empathy. Time management. Teamwork. Communication. Analysis. Patience. Collaboration. Helpfulness. Accountability.}
\vspace{0.2cm}
\cvitem{\textbf{Development Methodologies}}{ Scrum, Kanban, Extreme Programming. }
\vspace{0.2cm}
\cvitem{\textbf{Programming Concepts}}{Functional Programming, Object Oriented Programming, Concurrent and Parallel Programming, Generic Programming, Distributed computing, Test-driven Development, Object Oriented Design Patterns, Game Development, REST, Object Relational Mapping. }
\vspace{0.2cm}
\cvitem{\textbf{Programming Languages}}{Go, Erlang, Elixir, Ruby, Java, Python, Bash, JavaScript/Typescript, Racket, Scheme, SQL, C\#, C++, Objective-C, Swift, C, R, HTML/HTML5, CSS/CSS3, \LaTeX. }
\vspace{0.2cm}
\cvitem{\textbf{Software Frameworks, Tools and APIs}}{Ruby on Rails, Phoenix, Android, Dropwizard, Spring Boot, JQuery, React, React Native, iOS, Qt, Windows Phone, WindowsRT/Windows8, Django, Git, Linux. }
\vspace{0.2cm}
\cvitem{\textbf{Datastores}}{PostgreSQL, ElasticSearch, MySQL, Redis, RabbitMQ, Kafka, MongoDB. }
\vspace{0.2cm}
\cvitem{\textbf{Infrastructure Services}}{Amazon AWS (EC2, RDS, S3, Route53, ECS, SES, SQS, DynamoDB etc), Microsoft Azure, Linode, Digital Ocean, Firebase. }
\vspace{0.2cm}
\cvitem{\textbf{Infrastructure Tools}}{Terraform, Packer, Docker, Kubernetes, Mesos/Marathon, Puppet, Ansible, Chef, ELK. }
\vspace{0.2cm}
\cvitem{\textbf{Monitoring and Alerting}}{Prometheus, StatsD, Graphite, Datadog, Graphana, Sensu, New Relic, Sentry. }
\vspace{0.2cm}
\cvitem{\textbf{CI/CD}}{Jenkins, Drone, CircleCI, TravisCI. }

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{June, 2017 -- Present}{Senior Software Engineer}{\textsc{Meltwater}}{meltwater.com}{Berlin, Germany}{ Developing, programming and designing distributed cloud services and applications. Living the dream, in a well established agile and DevOps culture.}
\vspace{0.5cm}
\cventry{September, 2016 -- May, 2017}{Lead Software Engineer}{\textsc{Vispera Information Technologies}}{vispera.co}{Istanbul, Turkey}{ Lead Web, Cloud and Mobile team. Designed, architect and developed cloud and mobile solutions, end-to-end. Mentored and trained engineers. Ensured shipment of web, cloud and mobile products. }
\vspace{0.5cm}
\cventry{August, 2014 -- September, 2016}{Software Engineer}{\textsc{Vispera Information Technologies}}{vispera.co}{Istanbul, Turkey}{ Took full responsible for development of cloud and mobile services. Developed, programmed and designed several cloud services, backends and web applications. Designed, developed several mobile applications. Deployed and maintained several web applications and services. Helped to develop native desktop applications and services for internal usage and operations. Mentored and trained engineers. }
\vspace{0.5cm}
\cventry{October, 2012 -- May, 2016}{Junior Software/Product Engineer}{\textsc{Fazlamesai}}{fazlamesai.com}{Istanbul, Turkey}{ Took end-to-end responsibility, through life-cycle of several software products. Programmed, developed and helped to design mobile applications for various products. Programmed, developed and maintained various web services and web applications for various products. }

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2016--2017}{Master$'$s degree, Computer Engineering}{Bogazici University}{Istanbul, Turkey}
{\textbf{\textit{Not graduated}}}{}
\vspace{0.5cm}
\cventry{2010--2014}{Bachelor$'$s degree, Computer Science}{Istanbul Bilgi University}{Istanbul, Turkey}
{\textit{\textbf{GPA -- 3.92/4.0}}}{}
\vspace{0.5cm}
\cventry{2008--2010}{Bachelor$'$s degree, Physics}{Middle East Technical University}{Ankara, Turkey}
{\textbf{\textit{Not graduated}}}{}
\vspace{0.5cm}
\cventry{2006--2008}{Bachelor$'$s degree, Philosophy}{Galatasaray University}{Istanbul, Turkey}
{\textbf{\textit{Not graduated}}}{}
\vspace{0.5cm}
\cventry{2003--2006}{High School}{Izmir Turk Science High School}{Izmir, Turkey}
{\textit{GPA -- 4.55/5.0}}{}

\vspace{1cm}

%----------------------------------------------------------------------------------------
% AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}
\cvitem{June, 2014}{First place in program, class of 2014 at Istanbul Bilgi University}
\vspace{0.5cm}
\cvitem{June, 2014}{Second place in all programs of faculty, class of 2014 at Istanbul Bilgi University}
\vspace{0.5cm}
\cvitem{June, 2014}{Third place in all programs of university, class of 2014 at Istanbul Bilgi University}
\vspace{0.5cm}
\cvitem{2010--2014}{Full University Scholarship at Istanbul Bilgi University}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\cventry{June, 2015 -- May, 2016}{PsycUp}{}{Istanbul}{An online social media platform.}{Developed and maintained web application, front-end and services for platform using \textit{Ruby/Rails, jQuery, Bootstrap}. }
\vspace{1cm}
\cventry{January, 2015 -- May, 2016}{Q Content and Community}{}{Istanbul}{An online content publishing and community driven social media platform}{Developed and maintained web application, front-end and services for platform using \textit{Ruby/Rails, jQuery, Bootstrap}, programmed a RESTful JSON API for mobile clients. Contributed to development of mobile applications, mostly worked on \textit{Android/Java} client. }
\vspace{1cm}
\cventry{June, 2013 -- Present}{ymuse}{}{Istanbul}{A sophisticated client for ymuse.com (Turkish Music Database). Puts album presentation in the center. Shows new ways to explore music with a comfortable presentation}{Developed and maintained web application, front-end and services for platform using \textit{Ruby/Rails}, programmed a RESTful JSON API for mobile clients. Programmed and developed mobile applications, mostly worked on \textit{Android/Java} client and contributed to \textit{iOS/Objective-C} client of platform.}
\vspace{1cm}
\cventry{November, 2012 -- June, 2014}{TurkcellTV}{www.turkcelltv.com.tr}{Istanbul}{Video On Demand, Live TV streaming, social TV on multiple platforms (Web, iOS, Android)}{ Developed and maintained web service and HTTP API for platform written in \textit{Python/Django}. Programmed, developed and maintained \textit{Java/Android} client for platform.}
\vspace{1cm}
\cventry{November, 2012}{Bizimleye}{www.bizimleye.com}{Istanbul}{bizimleye is a social dining network that focused on subject matter and guest and brings people together at restaurants.}{Developed and maintain web application and web service for platform using \textit{Python/Django, JQuery.}}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Turkish}{Native}{}
\cvitemwithcomment{English}{Advanced}{}
\cvitemwithcomment{German}{Basic}{}

\vspace{2cm}

\section{Volunteer Works}
\cventry{April, 2013}{Free Software and Open Source Days 2013}{Organization Committee}{Istanbul, Turkey}{}{}
\cventry{April, 2012}{Free Software and Open Source Days 2012}{Organization Committee}{Istanbul, Turkey}{}{}
\cventry{April, 2011}{Free Software and Open Source Days 2011}{Volunteer Worker}{Istanbul, Turkey}{}{}
\cventry{2012--Present}{LKD (Linux Users Association)}{Member}{Istanbul, Turkey}{}{}
\cventry{September, 2011}{COLLNET 7. International Conference on Webometrics, Informetrics and Scientometrics (WIS) 2011}{Organization Committee}{Istanbul, Turkey}{}{}
\cventry{April, 2011}{Free Software and Open Source Days 2011}{Volunteer Worker}{Istanbul, Turkey}{}{}
\cventry{2011--Present}{Bugday Association for Supporting Ecological Living}{Member}{Istanbul, Turkey}{}{}
\cventry{2011--Present}{World Wildlife Fund}{Member}{Istanbul, Turkey}{}{}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Tango}{Lindy Hop}
\cvlistdoubleitem{Traveling}{Programming}
\cvlistdoubleitem{Learning}{Teaching}
\cvlistdoubleitem{Running}{Swimming}

\vspace{1cm}

%----------------------------------------------------------------------------------------
% REFERENCE SECTION
%----------------------------------------------------------------------------------------

\section{References}
\cventry{\textit{Meltwater}}{Necessary information will be provided at later stages}{}{}{Berlin, Germany}{}
\cventry{\textit{Vispera}}{Ceyhun Burak Akgül}{+90 (532) 362 59 25}{cb.akgul@vispera.co}{Istanbul, Turkey}{}
\cventry{\textit{Fazlamesai}}{Yusuf Boran Puhaloğlu}{+90 (532) 663 00 44}{boran@fazlamesai.com}{Istanbul, Turkey}{}
\cventry{\textit{Istanbul Bilgi University}}{Mehmet Gençer}{+90 (505) 410 66 02}{mgencer@bilgi.edu.tr}{Istanbul, Turkey}{}

\vspace{1cm}

%----------------------------------------------------------------------------------------

\end{document}
