\documentclass[12pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage[utf8x]{inputenc}

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% \usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
% \usepackage{hyperref}

\usepackage[scale=0.75]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3cm} % Un-comment to change the width of the dates column
% \setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, un-comment to adjust the width of the space allocated to your name

\firstname{Kemal} % Your first name
\familyname{Akkoyun} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Software Infrastructure Engineer / SRE}
\email{kakkoyun@gmail.com - +49 (173) 238 85 13}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Prints the CV title

\url{kakkoyun.me} \\
\url{github.com/kakkoyun} \\
\url{linkedin.com/in/kakkoyun} \\
\url{stackoverflow.com/story/kakkoyun} \\

\cvitem{}{\textit{Cloud Software Infrastructure Engineer and Site Reliability Engineer. }}
\cvitem{}{\textit{Mentor. Blogger and speaker. }}
\cvitem{}{\textit{Learning (by building) about Distributed Systems and Databases. Focusing on Observability, Reliability and Performance.}}
\cvitem{}{\textit{Introverted Human. Open Source Developer. Thanos Maintainer. Prometheus Contributor.}}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{July, 2019 -- Present}{Software Engineer}{\textsc{Red Hat}}{redhat.com}{Berlin, Germany}{ OpenShift Monitoring and Observability Platform Team Member. I help to build a large scale, real-time distributed database to store observability signals and infrastructure around it.}
\vspace{0.5cm}
\cventry{June, 2017 -- July, 2019}{Senior Software Engineer}{\textsc{Meltwater}}{meltwater.com}{Berlin, Germany}{ Developed, programmed, designed, maintained, and delivered event distributed cloud services, APIs, content ingestion pipelines, event ingestion pipelines, ETL systems, stream processing pipelines, serverless infrastructure, web services, and applications. Set up CI/CD pipelines and established the reliability and on-call workflows. Had been on Tier 1 on-call rotation. Trained and mentored engineers. }
\vspace{0.5cm}
\cventry{September, 2016 -- May, 2017}{Lead Software Engineer}{\textsc{Vispera Information Technologies}}{vispera.co}{Istanbul, Turkey}{ Lead Web, Cloud, and Mobile team. Designed and developed cloud and mobile solutions, end-to-end. Mentored and trained engineers. Ensured and supervised shipment of the web, cloud, and mobile products. Hired, mentored, and trained engineers. Set up the cloud infrastructure and delivery pipelines. Established the reliability and on-call workflows. }
\vspace{0.5cm}
\cventry{August, 2014 -- September, 2016}{Software Engineer}{\textsc{Vispera Information Technologies}}{vispera.co}{Istanbul, Turkey}{ Took full responsibility for the development of cloud and mobile services. Developed, programmed, and designed several cloud services, web services, and applications. Designed, developed several mobile applications. Deployed and maintained several web applications and services. Helped to develop native desktop applications and services for internal usage and operations. Mentored and trained engineers. }
\vspace{0.5cm}
\cventry{October, 2012 -- May, 2016}{Software/Product Engineer}{\textsc{Fazlamesai}}{fazlamesai.com}{Istanbul, Turkey}{ Took end-to-end responsibility, through the life-cycle of several software products. Programmed, developed, and helped to design mobile applications for various products. Programmed, developed, and maintained various web services and web applications for various products. }

\vspace{1cm}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2010--2014}{Bachelor$'$s degree, Computer Science}{Istanbul Bilgi University}{Istanbul, Turkey}
{\textit{\textbf{GPA -- 3.92/4.0}}}{}
\vspace{0.5cm}
\cventry{2016--2017}{Master$'$s degree, Computer Engineering}{Bogazici University}{Istanbul, Turkey}
{\textbf{\textit{Not graduated}}}{}
\vspace{0.5cm}
\cventry{2008--2010}{Bachelor$'$s degree, Physics}{Middle East Technical University}{Ankara, Turkey}
{\textbf{\textit{Not graduated}}}{}
\vspace{0.5cm}
\cventry{2006--2008}{Bachelor$'$s degree, Philosophy}{Galatasaray University}{Istanbul, Turkey}
{\textbf{\textit{Not graduated}}}{}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	OPEN SOURCE PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Significant Open Source Projects}

\cventry{June, 2019 -- Present}{Thanos}{}{Berlin}{Highly available Prometheus setup with long term storage capabilities. CNCF Incubation project.}{Mainter.}
\vspace{0.5cm}
\cventry{June, 2020 -- Present}{Prometheus}{}{Berlin}{The Prometheus monitoring system and time series database.}{Contributor.}
\vspace{0.5cm}
\cventry{August, 2018 -- Present}{Drone Cache}{}{Berlin}{A Drone plugin for caching current workspace files between builds to reduce your build times}{Maintainer.}
\vspace{0.5cm}

%----------------------------------------------------------------------------------------
% AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}
\cvitem{June, 2014}{Summa Cum Laude, Highest GPA in program, class of 2014 at Istanbul Bilgi University}
\vspace{0.5cm}
\cvitem{June, 2014}{Second highest GPA in all programs of faculty, class of 2014 at Istanbul Bilgi University}
\vspace{0.5cm}
\cvitem{June, 2014}{Third highest GPA in all programs of university, class of 2014 at Istanbul Bilgi University}
\vspace{0.5cm}
\cvitem{2010--2014}{Full University Scholarship at Istanbul Bilgi University}

\vspace{1cm}

%----------------------------------------------------------------------------------------
% REFERENCE SECTION
%----------------------------------------------------------------------------------------

\section{References}
\cventry{\textit{Red Hat}}{Frederic Branczyk}{Necessary contact information will be provided on demand}{}{Berlin, Germany}{}
\cventry{\textit{Red Hat}}{Ed Rooth}{Necessary contact information will be provided on demand}{}{Berlin, Germany}{}
\cventry{\textit{Meltwater}}{Sebastian Spier}{Necessary contact information will be provided on demand}{}{Berlin, Germany}{}
\cventry{\textit{Wooga}}{Leonid Batyuk}{Necessary contact information will be provided on demand}{}{Berlin, Germany}{}
\cventry{\textit{Vispera}}{Ceyhun Burak Akgül}{+90 (532) 362 59 25}{cb.akgul@vispera.co}{Istanbul, Turkey}{}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Turkish}{Native}{}
\cvitemwithcomment{English}{Advanced}{}
\cvitemwithcomment{German}{Basic}{}

\vspace{1cm}

\section{Volunteer Works}
\cventry{June, 2020}{CommunityBridge}{Mentor}{Berlin, Germany}{https://people.communitybridge.org/mentor/84363dc2-b7fa-4924-9026-bcbf265cec2e}{}
\cventry{June, 2020}{GoBridge}{Mentor}{Berlin, Germany}{}{}
\cventry{April, 2013}{Free Software and Open Source Days 2013}{Organization Committee}{Istanbul, Turkey}{}{}
\cventry{April, 2012}{Free Software and Open Source Days 2012}{Organization Committee}{Istanbul, Turkey}{}{}
\cventry{April, 2011}{Free Software and Open Source Days 2011}{Volunteer Worker}{Istanbul, Turkey}{}{}
\cventry{September, 2011}{COLLNET 7. International Conference on Webometrics, Informetrics and Scientometrics (WIS) 2011}{Organization Committee}{Istanbul, Turkey}{}{}
\cventry{April, 2011}{Free Software and Open Source Days 2011}{Volunteer Worker}{Istanbul, Turkey}{}{}
\cventry{2012--Present}{LKD (Linux Users Association)}{Member}{Istanbul, Turkey}{}{}
\cventry{2011--Present}{Bugday Association for Supporting Ecological Living}{Member}{Istanbul, Turkey}{}{}
\cventry{2011--Present}{World Wildlife Fund}{Member}{Istanbul, Turkey}{}{}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%  SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills, Merits and Faculties}

\cvitem{\textbf{Programming Concepts}}{Functional Programming, Object Oriented Programming, Concurrent and Parallel Programming, Generic Programming, Distributed computing, Test-driven Development, Object Oriented Design Patterns, Game Development, REST, Object Relational Mapping. }
\vspace{0.2cm}
\cvitem{\textbf{Programming Languages}}{Go, Elixir, Ruby, Java, Python, Bash, JavaScript/NodeJS, Typescript, Erlang, Racket, Scheme, SQL, C\#, C++, Objective-C, Swift, C, R, HTML/HTML5, CSS/CSS3, \LaTeX. }
\vspace{0.2cm}
\cvitem{\textbf{Software Frameworks, Tools and APIs}}{Ruby on Rails, Phoenix, Android, Dropwizard, Spring Boot, Gin, Gorm JQuery, AngularJS, Angular, React, React Native, iOS, Qt, Windows Phone, WindowsRT/Windows8, Django, Git, Linux. }
\vspace{0.2cm}
\cvitem{\textbf{Datastores}}{PostgreSQL, ElasticSearch, MySQL, Redis, RabbitMQ, Kafka, MongoDB. }
\vspace{0.2cm}
\cvitem{\textbf{Infrastructure Services}}{Amazon AWS (EC2, RDS, S3, Route53, ECS, SES, SQS, DynamoDB etc), Microsoft Azure, Linode, Digital Ocean, Firebase. }
\vspace{0.2cm}
\cvitem{\textbf{Infrastructure Tools}}{Terraform, Packer, Docker, Kubernetes, Mesos/Marathon, Puppet, Ansible, Chef, ELK. }
\vspace{0.2cm}
\cvitem{\textbf{Development Methodologies}}{ Scrum, Kanban, Extreme Programming. }
\vspace{0.2cm}
\cvitem{\textbf{Monitoring and Alerting}}{Prometheus, Thanos, StatsD, Graphite, Datadog, Graphana, Sensu, New Relic, Sentry. }
\vspace{0.2cm}
\cvitem{\textbf{CI/CD}}{Jenkins, Drone, CircleCI, TravisCI. }
\vspace{0.2cm}
\cvitem{\textbf{Soft Skills}}{ Open mindedness. Problem solving. Creativity. Leadership. Empathy. Time management. Teamwork. Communication. Analysis. Patience. Collaboration. Helpfulness. Accountability.}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	FREELANCE PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Freelance Projects}

\cventry{June, 2015 -- May, 2016}{PsycUp}{}{Istanbul}{An online social media platform.}{Developed and maintained web application, front-end and services for platform using \textit{Ruby/Rails, jQuery, Bootstrap}. }
\vspace{0.5cm}
\cventry{January, 2015 -- May, 2016}{Q Content and Community}{}{Istanbul}{An online content publishing and community driven social media platform}{Developed and maintained web application, front-end and services for platform using \textit{Ruby/Rails, jQuery, Bootstrap}, programmed a RESTful JSON API for mobile clients. Contributed to development of mobile applications, mostly worked on \textit{Android/Java} client. }
\vspace{0.5cm}
\cventry{June, 2013 -- Present}{ymuse}{}{Istanbul}{A sophisticated client for ymuse.com (Turkish Music Database). Puts album presentation in the center. Shows new ways to explore music with a comfortable presentation}{Developed and maintained web application, front-end and services for platform using \textit{Ruby/Rails}, programmed a RESTful JSON API for mobile clients. Programmed and developed mobile applications, mostly worked on \textit{Android/Java} client and contributed to \textit{iOS/Objective-C} client of platform.}
\vspace{0.5cm}
\cventry{November, 2012 -- June, 2014}{TurkcellTV}{www.turkcelltv.com.tr}{Istanbul}{Video On Demand, Live TV streaming, social TV on multiple platforms (Web, iOS, Android)}{ Developed and maintained web service and HTTP API for platform written in \textit{Python/Django}. Programmed, developed and maintained \textit{Java/Android} client for platform.}
\vspace{0.5cm}
\cventry{November, 2012}{Bizimleye}{www.bizimleye.com}{Istanbul}{bizimleye is a social dining network that focused on subject matter and guest and brings people together at restaurants.}{Developed and maintain web application and web service for platform using \textit{Python/Django, JQuery.}}
\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Traveling}{Whiskey}
\cvlistdoubleitem{Yoga}{Whiskey}
\cvlistdoubleitem{Dogs}{More dogs}
\cvlistdoubleitem{Lindy Hop}{Tango}
\cvlistdoubleitem{Running}{Swimming}

\vspace{1cm}

%----------------------------------------------------------------------------------------

\end{document}
